\TheTitle

### 2017-07-06 paper/lineval.tex
Breaking introduction into sections
Breaking the massive introduction into sections to match original paper

\ifdraft
        \documentclass[conference, draftclsnofoot, draft]{IEEEtran}
        \def\baselinestretch{1}
        \setlength{\marginparwidth}{2cm}
\else
        \documentclass[conference]{IEEEtran}
\fi

@@

% DAG model

@@

% Merge tree model

@@

% Evaluation

In order to determine the effectiveness of the merge-tree model on
comprehension and summarization of git repositories, we conducted a
controlled user study on 12 participants. The user study is a
mixed-methods study, with focus on the quantitative aspects in order to
capture how effective the \mt model, if it is, at improving the
correctness, accuracy, and time performance metrics of users when
performing summarization tasks. We use the qualitative questions as a
means of determine the preference of the participants, and what aspects
they preferred from each tool.

We formulate three research questions that this study is attempting to
answer;

\begin{RQ}
  \item

    Is the DAG able to provide users with an understanding of the events
    in a repository?

    Do \mt make a difference in the ability to summarize basic
    aggregated information?

    Do users prefer the \mt model to the DAG for summarization and
    comprehension tasks?

\end{RQ}

% Implementation

@@

\section{Results}
\label{sec:results}

>>>>

\ifdraft
        \documentclass[draft]{IEEEtran}
        \def\baselinestretch{1}
        % \setlength{\marginparwidth}{1.5cm}
\else
        \documentclass[conference]{IEEEtran}
\fi

@@

@@

One major challenge with visualizing the arrival of commits to a repository is that
Git does not store the date that a commit was merged into another branch, including
the master branch. To complicate the problem, the DAG only has references to the
ancestors of a commit (a model necessary for the operation of Git), but maintainers
would prefer knowing the path a commit followed to reach the master repository.
Tracing a path that any commit followed to the master repository would imply that
for any given merge, it would be possible to know which commits were merged. A user
could inspect the commits that arrived into the master branch within a given
time-frame by checking which commits were merged during that time-frame.

This paper makes two contributions; first, we describe a method of converting the
DAG of the Linux repository into a tree, or \emph{merge-tree} of the repository,
that represents the path used by a commit to reach the master branch; second, we
present a method to inspect and visualize the history of merges in the Linux project
using the merge-tree model.

These methods and visualizations are implemented in a web-based tool called
\tool\footnote{\tool is currently available at \url{http://li.turingmachine.org}}.
Our visualizations and tool provide information about the location of any given
commit or merge in its respective merge-tree, the files edited, the modules edited,
and the commit message. \tool allows users to apply various filters, including the
release version, along with a keyword or phrase from the log preview, the name of
the author, or the commit ID. The user can request all merges made by Linus that
contain a commit or inner merge that matches the search query, or just the commits
and merges that match the query.

\section{\mt Model}
\label{sec:mt_model}

@@

\section{Design and Implementation}
\label{sec:design_and_implementation}

@@

\subsection{Results}
\label{sec:results}
